---
title: "Introduction to ChIAnalysis"
author: "Eric Fournier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ChIAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

ChIAnalysis: A toolset for analyzing ChIA-PET data
====================================================================

Eric Fournier, Audrey Baguette, Steve Bilodeau and Arnaud Droit.

This package is distributed under the Artistic license 2.0.
You are free to use and redistribute this software. 

ChIA-PET experiments provides comprehensive information about the 
3D-interactions of the genome which are mediated by a protein of interest.
While such interactions are interesting on their own, placing them
in the context of an overall interaction graph can lead to novel
biological insights. ChIAnalysis is designed for such a purpose.

This vignette will introduce the main features of the ChIAnalysis package.

### Loading the ChIAnalysis package

```{r libraryLoad, warning=FALSE}
library(ChIAnalysis)
```

### Introduction

To use ChIAnalysis, you will require a seven column, tab-separated file 
containing the coordinates of the first interaction point in the first three 
columns, the coordinates of the second interaction point in the next three, 
and the number of reads supporting this interaction in the seventh column.

|chr1|start1|end1|chr2|start2|end2|Nb Reads|
|----|------|----|----|------|----|--------|

The basic usage involves only 5 function calls.
```{r basic_usage, eval = FALSE}
    # Build a ChIAParameters object with annotation information.
    chia_params = build_chia_params(biosample = "GM12878",
                                    genome.build = "hg19")
    
    # Add any annotation made available by ENCODE
    chia_params = add_encode_data(chia_params)
    
    # Load the input interactions
    chia_obj = load_chia(input_file)
    
    # Add the relevant annotations.
    chia_obj = annotate_chia(chia_obj, chia_params)
    
    # Perform all relevant analyses.
    analyze_chia_pet(chia_obj, chia_params)
```

### Basic usage

#### Adding annotation

Blah.

#### Subsetting the ChIA object.

Bleh!

### Advanced usage

#### Producing custom plots

Bloh!